Potential involvement of the Frank-Starling mechanism in reduced stroke volume variability observed in a murine model of heart failure with reduced ejection fraction

### 2023-03-26 Manuscript/manuscript.tex
update

\begin{figure}[h!]
    \begin{tabular}{cc}
        A & B \\
        \includegraphics[width=3in]{Fig02_A.pdf} &
        \includegraphics[width=3in]{Fig02_B.pdf}
    \end{tabular}
    \caption{A) Poincairé-plot indices of heart period variability for control (blue) and HFrEF (orange) groups. B) Poincairé-plot indices of stroke volume variability for control (blue) and HFrEF (orange) groups. Brackets indicates statistically significant difference.}
    \label{fig:fig02}
\end{figure}

>>>>

\begin{figure}[h!]
    \begin{tabular}{cc}
        A & B \\
        \includegraphics[width=3in]{Fig02_A.pdf} &
        \includegraphics[width=3in]{Fig02_B.pdf} \\
        C & D \\
        \includegraphics[width=3in]{Fig02_C.pdf} &
        \includegraphics[width=3in]{Fig02_D.pdf}
    \end{tabular}
    \caption{A) Representative Poincairé plots of heart period variability for mice in the control (blue) and HFrEF (orange) groups. B) Representative Poincairé plots of stroke volume variability for mice in the control (blue) and HFrEF (orange) groups. C) Poincairé-plot indices of heart period variability for control (blue) and HFrEF (orange) groups. D) Poincairé-plot indices of stroke volume variability for control (blue) and HFrEF (orange) groups. Brackets indicates statistically significant difference.}
    \label{fig:fig02}
\end{figure}
